The \textsc{sherpa}~\cite{SHERPA} and \textsc{powheg}~\cite{POWHEG} generators
are interfaced with \textsc{pythia8}~\cite{PYTHIA8} to produce the diboson
($WW$, $WZ$ and $ZZ$ processes) \gls{mc} samples. After taking into account
possible inclusive cross section differences of the two generators, the full
difference in yields in each $\met$ bin of the two generators is taken as the
systematic uncertainty and added in quadrature with a 6\% theory uncertainty on
the \gls{nlo} cross section.
\begin{description}[font=\normalfont]
\item[diboson\_Sys:] This parameter accounts for the diboson systematic variations.
\end{description}
\cref{tab:diboson_sys_2016} reports the diboson uncertainties evaluated from the
comparison between the two generators for the different exclusive regions
EM1-EM10 defined in the analysis for the signal region and the different control
regions. The diboson systematic uncertainty is observed to grow at higher
missing transverse energy, where in particular the two generators can differ by
up to 31\% in the signal region. The generators are however in very good
agreement at lower missing energies. In the 2015 analysis the agreement between
the two generators ranged between 5\% and 25\% for $\met$ bins below 800~GeV
increasing up to 50\% above 800~GeV. The diboson systematic uncertainties in
this version of the analysis are generally lower due to the higher order of the
Monte Carlo generators used.
\begin{table}[!htb]
  \centering
  \resizebox{\linewidth}{!}{
  \begin{tabular}{lcccccccccc}
    \toprule
    \multicolumn{11}{c}{Diboson Uncertainty} \\
    \midrule \midrule
    \quad & EM1 & EM2 & EM3 & EM4 & EM5 & EM6 & EM7 & EM8 & EM9 & EM10 \\
    \midrule
    SR & 3.6 & 1.6 & 0.4 & 3.3 & 7.3 & 11.3 & 15.3 & 19.3 & 23 & 31 \\
    $\crele$ & 2.5 & 1.0 & 0.4 & 2.5 & 5.3 & 8.2 & 11.0 & 13.9 & 16.7 & 22.4 \\
    $\crwmn$ & 0.4 & 0.2 & 0.0 & 0.3 & 0.8 & 1.2 & 1.6 & 2.0 & 2.4 & 3.3 \\
    $\crtop$ & 1.2 & 2.1 & 3.1 & 4.5 & 6.5 & 8.4 & 10.3 & 12.2 & 14.2 & 18.0 \\
    $\crzmm$ & 0.9 & 0.6 & 0.2 & 0.2 & 0.8 & 1.4 & 2.1 & 2.7 & 3.3 & 4.5 \\
    \bottomrule
  \end{tabular}}
\caption{Relative systematic uncertainties in \% on the diboson background as a
  function of the exclusive bins EM1-EM10 defined in the analysis for the signal
  region and the different control regions as evaluated from the comparison
  between the generators. These values are then added in quadrature with a 6\%
  uncertainty on the \gls{nlo} diboson cross section.}
  \label{tab:diboson_sys_2016}
\end{table}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../search_for_DM_LED_with_ATLAS"
%%% End:
