\begin{description}[font=\normalfont]
\item[syst\_MUON\_ID:] This nuisance parameter takes into account the impact of
  the uncertainty from the measurement of the inner detector track momentum on
  the final muon momentum.
\item[syst\_MUON\_MS:] This parameter accounts for the impact of the uncertainty
  from the measurement of the muon system track momentum on the final muon
  momentum.
\item[syst\_MUON\_EFF\_STAT (SYS):] This parameter accounts for the
  statistical (systematic) uncertainty on the data to Monte Carlo muon
  reconstruction scale factor.
\item[syst\_MUON\_EFF\_STAT (SYS) \_LOWPT:] This parameter accounts for the
  statistical (systematic) uncertainties on the data to Monte Carlo muon
  reconstruction scale factor for low $\pt$ muons.
\item[syst\_MUON\_SCALE:] This parameter accounts for the uncertainty on the
  muon momentum scale.
\item[syst\_MUON\_BADMUON\_STAT (SYS):] This parameter models bad muon
  statistical (systematic) uncertainties for high $\pt$ muons (above 100~GeV)
  due to the specific muon working point used for high $\pt$
  muons~\cite{MuonCalib}.
% \item[syst\_MUON\_BADMUON\_SYS:] This parameter describes bad muon systematic
%   uncertainties.
% \item[syst\_MUONS\_EFF\_TrigSystUncertainty:] This parameter accounts for
%   muon trigger uncertainties.
\item[syst\_MUON\_SAGITTA\_RESBIAS (RHO):] The muon momentum measurement relies
  on the precise knowledge of the sagitta of the muon track between muon
  stations. The calibration constants used to calibrate the muon Monte Carlo are
  derived from $Z \rightarrow \mu \mu$ and $J/\psi$ data in bins of $\eta$ and
  $\phi$. These parameters model uncertainties on the calibration procedure and
  residual charge dependent bias in muon momentum scale.
%   This parameter models variations in the
%   scale of the momentum based on the residual charge-dependent bias after
%   correction.
% \item[syst\_MUON\_SAGITTA\_RHO:] This parameter accounts for variations in the
%   scale of the momentum based on combination of correction on combined ($Z$
%   scale) and recombination of the corrections.
\item[syst\_MUON\_TTVA\_STAT (SYS):] This parameter models the statistical
  (systematic) uncertainties on the efficiency of the muon track-to-vertex
  matching efficiency.
  % This parameter accounts for statistical
  % uncertainties on the track-to-vertex association.
% \item[syst\_MUON\_TTVA\_SYS:] This parameter models systematic uncertainties on
%   the track-to-vertex association.
\end{description}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../search_for_DM_LED_with_ATLAS"
%%% End:
