In this analysis only a single overall scale factor $k^\mathrm{V + jets}$ is
considered (see \cref{sec:fit-strategy}), it scales up or down the entire $W$ +
jets and $Z$ + jets predictions by the same amount in all the $\met$ bins
defined in the analysis. This means effectively that the momentum spectrum of
the vector boson or its experimental proxy, the missing energy, is taken from
Monte Carlo simulation. In the 2015 analysis one independent scale factor for
each $\met$ bin was used in order to account for the limited knowledge of the
shape of the $\pt$ spectrum of the gauge boson. In this version of the analysis
this is accounted for using instead theoretical nuisance parameters taken from
Ref.~\cite{VplusJetsCorrections} associated with the V + jets normalization
strategy given in \cref{sec:corrections-vjets}. These nuisance parameters allow
the shape of the boson $\pt$ to change with respect to corrected Monte Carlo
simulation within certain allowed theory boundaries and in the global fit
implemented in the analysis are labeled as:
% In order to account for possible mismodelings associated with the higher order
% corrections to the V + jets samples described in \cref{sec:corrections-vjets},
% the following nuisance parameters are introduced in the statistical model and
% thus constrained by the global fit described in \cref{sec:fit-strategy}:
% \begin{description}[font=\normalfont]
% \item[$\delta_1 k_\mathrm{NLO}$:] Accounts for uncertainties in the
%   normalization of the vector boson $\pt$ distribution due to \gls{qcd} scale
%   variations.
% \item[$\delta_2 k_\mathrm{NLO}$:] This parameter accounts for shape
%   uncertainties of the vector boson $\pt$ distribution due to \gls{qcd} scale
%   variations.
% \item[$\delta_3 k_\mathrm{NLO}$:] This parameter accounts for the correlation of
%   \gls{qcd} uncertainties in the different V + jets processes.
% \item[$\delta_1 k_\mathrm{EW}$:] This parameter estimate the uncertainty of
%   unkown high $\pt$ \gls{ew} effects beyond \gls{nnlo}.
% \item[$\delta_2 k_\mathrm{EW}$:] This parameter accounts for unknown terms in
%   the \gls{nlo} approximation at high $\pt$ and for \gls{nnlo} effects that
%   might become relevant when hard contributions dominate.
% \item[$\delta_3 k_\mathrm{EW}$:] This term accounts for the limitations of the
%   Sudakov approximation.
% \item[$\delta_3 k_\mathrm{mix}$:] The \gls{qcd} and \gls{ew} are treated as
%   separate corrections, this term accounts for unknown interference terms not
%   taken into account.
% \end{description}
% \note{Probably for consistency it is better to switch to the following but need
%   to find out what are the extra two NP}
\begin{description}[font=\normalfont]
\item[vjets\_d1K\_NLO:] Accounts for uncertainties in the normalization of the
  vector boson $\pt$ distribution due to \gls{qcd} scale variations.
\item[vjets\_d2K\_NLO:] This parameter accounts for shape uncertainties of the
  vector boson $\pt$ distribution due to \gls{qcd} scale variations.
\item[vjets\_d3K\_NLO:] This parameter accounts for the correlation of \gls{qcd}
  uncertainties in the different V + jets processes.
\item[vjets\_d1kappa\_EW:] This parameter estimate the uncertainty of unknown
  high $\pt$ \gls{ew} effects beyond \gls{nnlo}.
\item[vjets\_d2kappa\_EW\_eej:] This parameter accounts for unknown terms in the
  \gls{nlo} approximation at high $\pt$ and for \gls{nnlo} effects that might
  become relevant when hard contributions dominate. It is used for the Z + jets
  processes. \pagebreak[4]
\item[vjets\_d2kappa\_EW\_evj:] This parameter accounts for the same effects as
  the previous one but it is used to constrain the W + jets processes.
\item[vjets\_d3kappa\_EW\_eej:] This term accounts for the limitations of the
  Sudakov approximation for the Z + jets processes.
\item[vjets\_d3kappa\_EW\_evj:] This term accounts for the limitations of the
  Sudakov approximation for the W + jets processes.
\item[vjets\_dK\_NLO\_mix:] The \gls{qcd} and \gls{ew} are treated as separate
  corrections, this term accounts for unknown interference terms not taken into
  account.
\end{description}
% Since the following parameters:
% \begin{itemize}
% \item vjets\_d2kappa\_EW\_eej
% \item vjets\_d2kappa\_EW\_evj
% \item vjets\_d3kappa\_EW\_eej
% \item vjets\_d3kappa\_EW\_evj
% \end{itemize}
Since both the vjets\_d2kappa\_EW\_eej and vjets\_d2kappa\_EW\_evj and both the
vjets\_d3kappa\_EW\_eej and vjets\_d3kappa\_EW\_evj parameters all describe
subleading unknown effects they are treated with independent nuisance parameters
for each process in the fit. The other parameters are treated as correlated
between the V + jets processes and vector boson $\pt$ but independent from one
another. The nuisance parameters are applied by re-weighting each event based on
the theory input of \cref{sec:corrections-vjets}, in particular up and down
variation histograms of the $\pt$ distributions of the vector boson are obtained
applying an event weight and treated in a consistent way to other normalization
and shape uncertainties.

Due to the limited Monte Carlo statistics, statistical fluctuations are possible
in the \gls{qcd} correction evaluations. For this reason a linear fit is applied
to the ratio of the differential cross sections in the \textsc{sherpa} \gls{mc}
and the V + jets theory prediction. The ``vjets\_QCDSmoothing'' nuisance
parameter is then introduced in order to take into account uncertainties coming
from this fit.
%%% local Variables:
%%% mode: latex
%%% TeX-master: "../search_for_DM_LED_with_ATLAS"
%%% End:
