The Standard Model process $\znunu$~+~jets where the neutrinos escape detection
generating large $\met$ is experimentally similar to signal events in the search
for BSM physics with a monojet signature in the final state. This process
constitutes an irreducible background and is the largest background in the
monojet analysis. The key to estimate the $\znunu$~+~jets background is to be
able to predict the momentum spectrum of the Z boson and, since this is assumed
to be equal to the $\met$, the amount of missing transverse energy. The control
regions defined in later sections provide ways to derive the $Z$ boson momentum
using data control regions.

The second biggest source of background with a monojet topology is the
$W (\rightarrow \ell \nu)$~+~jets, where $W (\rightarrow \tau \nu)$~+~jets, in
which the $\tau$ decays hadronically, it gives the highest contribution to this
class of events. The $W (\rightarrow \ell \nu)$~+~jets events with $\ell = e$ or
$\mu$ can fake a monojet signature if the lepton escapes the detector acceptance
or has a quality that is lower than the quality of the lepton veto criteria.

Other background processes are di-boson, $t \bar{t}$ and single top
processes. Multi-jet production from QCD processes where one or more jets are
mis-reconstructed leading to high $\met$ represent a small source of
background. Finally \gls{ncb} coming from cosmic particles, detector noise and
beam-induced background can give rise to fake jets and consequently to $\met$.
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../search_for_DM_LED_with_ATLAS"
%%% End:
