\gls{mb} events are soft ($\pt < 2$~GeV) inelastic interactions which constitute
a significant fraction of the hadron-hadron collisions. Understanding \gls{mb}
processes is therefore important for precision measurements of hard scatter
interactions. Perturbative \gls{qcd} is commonly used to describe parton
interactions when possible and non-perturbative \gls{qcd} for low $\pt$
processes. The free parameters of these models (\emph{tune parameters}) need to
be tuned in the \gls{mc} generators in order to replicate experimental
data. These variation of these parameters may lead to different number of
generated events in the \gls{mc} samples and thus to uncertainty in the
acceptance. Five tune parameters have been varied in order to account for
uncertainties from:
\begin{itemize}
\item Underlying event effects.
\item Jet structure effects.
\item Aspects of the MC generation that provide extra jet production.
\end{itemize}
For each ADD model, ten systematic samples are produced and analyzed at the
truth level, the effect of the acceptance is evaluated in the different bins
used in the analysis. The final uncertainty in each bin is a common envelope
valid for the different extra dimensions models (from ADD n = 2 to ADD n = 6),
the results are summarized in Table~\ref{tab:add_tune_scale}.
\begin{table}[!ht]
  \centering
  \resizebox{\linewidth}{!}{\begin{tabular}{lcccccccccc}
    \toprule
    \multicolumn{10}{c}{Initial and Final State Radiation} \\
    \midrule \midrule
    $\met$~[GeV] & 250-300 & 300-350 & 350-400 & 400-500 & 500-600 & 600-700 &
                                                                               700-800
 & 800-900 & 900-1000 & 1000-3000 \\
    $\Delta A(\%)$ & 11 & 11 & 8 & 7 & 7 & 10 & 13 & 18 & 13 & 9 \\
    \bottomrule
  \end{tabular}}
  \caption{Tune initial and final state radiation uncertainties in \% on the
    acceptance of the different signal region $\met$ bins in the analysis. The
    final value is a common envelope valid for all the ADD models between n = 2
    and n = 6 dimensions.}
  \label{tab:add_tune_scale}
\end{table}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../search_for_DM_LED_with_ATLAS"
%%% End:
