A \gls{cr} is a region of the phase space where the signal contribution is
negligible but the event selections are similar to those of the signal region so
that the normalization of the backgrounds in the signal region can be deduced
from observed number in the control regions. The main reason to define control
regions is to compute and check the agreement in shape and normalization between
MC simulations and data in reconstructed kinematic quantities. The $V$ + jets,
where $V$ is either a $W$ or a $Z$ vector boson, constitutes the main background
of the monojet analysis. The Monte Carlo simulations for the $V$ + jets
processes are generated using SHERPA~\cite{SHERPA} with 0, 1 or 2 jets at
\gls{nlo} and 2 or 4 jets at \gls{lo}. A pure \gls{mc} estimation of these
processes, suffers from theoretical uncertainties like the limited knowledge of
the \glspl{pdf}, limited order accuracy of the Monte Carlo generators and
experimental uncertainties related to the jet energy scale and luminosity
determination. In order to estimate the contribution of these backgrounds in the
SR, a \emph{data driven} technique is used. The method aims at reducing the
systematic uncertainties by relying on information from data in the \glspl{cr}
rather than on \gls{mc} simulations. It can be divided in three major steps:
\begin{itemize}
\item Define CRs to select $V$ + jets event in data.
\item Calculate a transfer factor from MC predicted events in the \gls{cr} to
  background estimates in the \gls{sr}\@.
\item Apply the transfer factor to the observed events in the \gls{cr} to obtain
  the estimate number of events from the process in the \gls{sr}\@.
\end{itemize}
The CRs used to constrain the $V$ + jets backgrounds have an event selection
that differs from the SR only in the lepton veto and the missing transverse
momentum calculation. Owing to the different lepton selections the \glspl{cr}
and \glspl{sr} are orthogonal and a minimum contribution from a monojet-like
signal is expected.
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../search_for_DM_LED_with_ATLAS"
%%% End:
