The \gls{atlas} detector is a multipurpose detector used for precision
measurements of a wide range of Standard Model processes and the search for new
decay channels of the Higgs boson and beyond the Standard Model phenomena such
as supersymmetry, extra dimensions or dark matter particles.

The Tile Calorimeter is the hadronic calorimeter covering the most central
region of the \gls{atlas} detector up to $|\eta| < 1.7$. It plays a vital role
in measuring the energy of jets and missing energy used in this thesis to search
for \gls{susy} and extra dimensions. To this end, an understanding of the
electronic noise inside the calorimeter is crucial as it affects the signal left
by the particles crossing the calorimeter and must be known precisely. The exact
noise level per calorimeter cell is used as an input to the algorithm that
identifies significant calorimeter energy deposits and then identifies and
measures jets, electrons and taus. Part of the work presented in this thesis was
to update, monitor and study the noise calibration constants for the Tile
Calorimeter to allow for precise reprocessing of the 2011 data and used for
precision measurements. During these studies unexpected variations over time in
the cell noise were observed. Further investigation led to discover that the
tile noise filter, an algorithm used to mitigate the effect of coherent noise,
was not behaving as expected in some situations significantly affecting
approximately 5\% of the cells in the TileCal.

This thesis presented two searches for \gls{bsm} physics in \gls{atlas}. The
first one used the 2015 data corresponding to an integrated luminosity of
3.2~$\ifb$ where for the first time the monojet analysis was used to set limits
on compressed light squark-neutralino models. Selections adapted to the specific
characteristics of this signal were studied. It was shown that the generic
approach provided by the global fit gives better sensitivity to this new signal
than a single signal region with asymmetric jet and $\met$ cuts. Several jet
veto criteria were studied since the \gls{bsm} compressed \gls{susy} scenario
probed in this thesis is the most sensitive to this type of cuts. No significant
excess in the data compared to the \gls{sm} predictions has been found thus the
results have been translated into model independent upper limits on the visible
cross section with a 95\% \gls{cl} and into model dependent limits in terms of
squark pair production with $\squarkprod$. Squark masses up to 608~GeV for
$\msquark - \mneutralino = 5$~GeV are excluded. The study of the 2015 dataset
extends limits shown in \cref{fig:susy_exclusion} that are provided by the more
classical approach to \gls{susy} searches.

The second analysis presented in this thesis uses the combined 2015 + 2016
dataset corresponding to an integrated luminosity of 36.1~$\ifb$ which was used
to explore the presence of large extra dimensions in the \gls{add} model
scenario. A good agreement between data and Standard Model prediction is
observed and no significant excess in data is seen thus the results are
translated in 95\%~\gls{cl} lower limits on the effective Planck scale
$\md$. Values of $\md$ of 7.7 and 4.8~TeV for two and six extra dimension
hypotheses are excluded, significantly improving the results obtained by
previous work. Future versions of this analysis will benefit from an increased
dataset. Including 2017, the data collected by \gls{atlas} during run 2 amounts
to approximately $70~\ifb$, almost doubling the luminosity used in this thesis.
However any significant improvement beyond the limits presented in this work
will require very substantial amount of additional data. Assuming that the
sensitivity to \gls{add} models is limited by statistical uncertainties on the
background, which is an optimistic assumption, we estimate from
\cref{eq:181,eq:117} that a doubling of the integrated luminosity would only
lead to a 10\% or less improvement on the limits on $\md$ (due to the high
exponent in the power dependence between $\md$ and the production cross
section).

The sensitivity to squarks in the compressed squark-neutralino model is
dominated by intermediate $\met$ bins, where the systematic uncertainty on the
background is more dominant than at high missing energies. Therefore significant
improvements in squark-neutralino sensitivity will require better background
calculations and reduced systematic uncertainties in addition to a simple
increase in integrated luminosity.
% Naturalness suggests that supersymmetric standard model partners are expected at
% the TeV scale, with the high luminosity foreseen in 2016 it will be possible to
% test experimentally the squark pair production with masses at that scale.
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../search_for_DM_LED_with_ATLAS"
%%% End:
